### 2022-04-14 paper1.tex
copyedits, add desc stat table

New sources of digital trace data have led to vast possibilities for social
science research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
Digital trace data are the expansive volumes of information that are now
available with the introduction and widespread adoption of the internet and
include sources such as social media sites, search data, blogs, administrative
data on websites, the internet archives, etc. In short, digital trace data are
the crumbs that are left as a person peruses and interacts in digital spaces.
Scholars have noted that these data provide many new research avenues for social
scientists because they are always on, non-reactive to a researcher's
observation, and very often capture social interactions and relationships, but
warn they can be inaccessible, non-representative, and be prone to drifting due
to algorithmic confounding\citep{salganikBitBitSocial2017}. Before
overenthusiastically embracing these sources and integrating them into our big
data toolkits, social scientists must clearly establish parameters under which
these data sources are appropriate, and for which questions they are useful
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one can ignore
foundational issues of measurement and construct validity and reliability and
dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}.

@@

Building on prior research outlining the various issues with different sources
of big data
\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
paper evaluates the construct validity of Google Search Trends as an indicator
of three different cases, namely attitudes, disease prevalence and political
preferences. These three cases will be tested using attitudinal indicators from
the %NORC General Social Survey, CDC \citeyearpar{vaches_data} and New York
Times \citeyearpar{mask_data}, health indicators from the CDC
\citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
\citeyearpar{covid_data}, and political indicators from the historical US
Presidential Election results \citeyearpar{pres_data}. % , and the American
National Election Survey \citeyearpar{anes_data}. This paper will contribute
guidance for creating standards of how to use Google Trends for social research,
and identify potential pitfalls that can compromise the analysis including the
focus of this paper, which shows that Google Trends has a lack of ecological
validity.

@@

I will use three categorizations of ways I propose Google Trends could be
utilized for social scientific usage. First, I test Google Trends as an
indicator of attitudinal indicators. After
\citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
utilize the ever-expanding world of big data, Google trends began slowly
appearing as a data source in sociological and social science research. From
research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020},
protest and anti-Muslim sentiment
\citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural interest.
Extending into social networks and culture,
\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how they saw 'culture' spreads around the globe through the proliferation of
search terms.

@@

Google Search Trends have been utilized to estimate disease prevalence and
population throughout the health sciences. While much of this research has
focused on the COVID-19 pandemic \citep{jimenez_etal20,
jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020,
mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020,
todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021}, other
research has investigated Google Trends as indicators of wellbeing
\citep{brodeurCOVID19LockdownsWellbeing2021,
carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020}, suicidality
\citep{burnettTimeTrendsPublic2020}, vaccination uptake
\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess a
correlation of \> .70 between the IV and DV, "demonstrating the vast potential
of Google Search as a proxy for monitoring population health" (p. 3) based on
assumptions that individuals search because of self-diagnosis and to identify
possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.

@@

Various sources have also used Google Trends to forecast political elections and
political attitudes \citep{wolfTrendingRightDirection2018}. For instance,
\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate Elections
relate to attention measured by search traffic.
\citet{pradoromanGoogleTrendsPredictor2020} demonstrate how Google Search trends
successfully predicts presidential election results in both the United States
and Canada. Finally, the OECD Development Centre is investigating how Google
data can help elucidate governments' approval in Latin America
\citep{montoyaUsingGoogleData2020}. Overall, the papers cited here find
favorable relationships between Google Trends and voting outcomes and claim that
it is also a valid measure of public attention.

@@

While Google Trends has not been widely used or validated by social scientists,
I am not the first author to investigate its validity. Some researchers have
cautioned against the wide usage of Google Search Trends. For instance,
\citet{asseoTrackingCOVID19Using2020} concludes in their research on COVID-19
case rates and Google searches that the correlation is often spurious and due to
confounding. They even explain that "searches would result not only from
self-symptoms, but also from interest elicited by media coverage"
\citep[][p.1]{asseoTrackingCOVID19Using2020}.

@@

\citet{cebrian_domenech22} emphasize in their research that there are some
non-negligible issues with the measurement of Google Trends, pointing to errors
within the purview of accuracy, completeness, consistency, and validity, as
outlined in \citet{KarrDataQuality}. % I know it is basic stats, but I would
provide a footnote explaining each of your terms. Here, these line up with
mainline stats but disciplines vary. \citet{cebrian_domenech22} point not only
to meta issues like the lack of transparency into the sampling methods and
population coverage, but they identify real differences in the data provided by
the Google Trends API for the same researcher-entered query, pointing to likely
internal process used by Google to sample their data to compute the trends.
These authors show that the variability of the results over time for the same
query can alter the results of analysis and forecasting significantly. While the
issue of unreliability isn't unique to the Google Trends API,
\citet{cebrian_domenech22} propose caution in the use of this digital trace data
for other researchers until further research can determine the root cause for
the inaccuracies.
% Yes, big issue. But, it is also seen in machine learning, survey 
% administration, etc. I’d assume one solution for dealing with fiddly 
% output is to just sample repeatedly and do some sort of average, 
% perhaps with a correction if the direction of the error is non random.

Finally, it is important to note that most of the research using Google Trends
as digital trace data do so to indicate population's \textit{attention} to a
search query. Because % I’d also say, the population is examined differently. It
is really a population of action remnants being used to get at a population of
people, which is presumed to be represented online. searches can be done with
many different intentions, such as information gathering, navigational purposes,
etc., it may be hard to declare that an overall level of engagement with a topic
on Google Search may be indicative of anything more than interest
\citep{da2011search}. To reference Clifford Geertz's invocation of Ryle, we only
know that the search was performed, not whether it indicated a digital wink or
twitch \citeyearpar{geertz1973thick}.
% For a soc audience some sort of reference to the dilemma of interpretation would be interesting.

@@

To test how well Google Trends can be used to indicate other measures, I use
various tests to validate the criterion validity of the trends. Criterion
validity measures how well one measure, an operationalization of a specific
construct, is able to predict a theoretical representation of the construct —
the criterion. For this article, I employ concurrent criterion validity which
looks at how Google Trends can predict various criterions in the same time
scale. I gathered geolocated social science data across multiple sources to
address the three areas of inquiry for this paper.  Table
\ref{tab:data-sources-table} outlines which data sources I use in this project
and which trends are matched to each source.

\input{tables/paper1/data-sources-table}

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification o "similar population clusters"
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo}.

@@

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse
Survey (HPS) and the 2019 American Community Survey (ACS) 1-year Public Use
Microdata Sample (PUMS) to measure U.S. residents’ intentions to receive the
COVID-19 vaccine if available during May 26, 2021 – June 7, 2021. This dataset
consists of 3,148 observations, one for each U.S. County. The variable measures
the percent of adults in the county who describe themselves as “unsure”,
“probably not”, or “definitely not” going to get a COVID-19 vaccine once one is
available to them. The variable ranges from 4.99\% to 32.33\%.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata, a global online market research firm, for the New York Times from July 2
through 14, 2020 \citep{mask_data}. 250,000 survey respondents were asked, "How
often do you wear a mask in public when you expect to be within six feet of
another person?". The NYT weighted each response to create a county level
measure of what percent of the county never, rarely, sometimes, frequently, and
always wore a mask when in public. This dataset consists of 3,148 observations,
one for each U.S. County included in the sample. This measure is purposed to
estimate the percent of adults in the county who never or rarely wear a mask
(range = 0.10\% to 55.80\%).

@@

I also use U.S. COVID-19 rates to validate health and disease related topics. I
retrieve U.S. county-level COVID-19 rates from \citet{covid_data}, who compile
this data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test %
Also blatant political interference in some places, which is probably worth
acknowledging. \citep{gu22, cdc20a} However, it is the best measure we have of
actual case rates without extensive adjustments. Case Rate is measured as number
of cases per 100,000 population. Observations vary from a minimum of zero to a
maximum of 1460.46 for each Monday from January 27, 2020, through December 27,
2021. There are 285,986 cases across 3,136 counties and 101 dates. Missing data
were interpolated using The Zoo package for R \citep{zoo}.

@@

In addition to specific measures of interest, I also gathered data on
potentially confounding variables. The first Seven of these variables come from
the 2010-2019 5-year American Community Surveys \citep{acs2019, acs2018,
acs2017, acs2016, acs2015, acs2014, acs2013, acs2012, acs2011, acs2010}. These
data include total population, population density, unemployment rate for those
sixteen years old and over, median county income, average commute time, percent
of households living under the poverty line, and percent above 65 years old. In
addition, some models employ the U.S. Current Population Survey \& American
Community Survey Geographic Estimates of Internet Use, 1997-2018
\citep{internet_use} to estimate households with broadband internet
subscriptions. This final variable is an attempt to capture the latent
propensity to use the internet for information search.

@@

As an additional criteria to evaluate the strength of the relationships, I
employ multiple linear regression (for cross-sectional datasets) and fixed
effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
datasets) to identify the strength of relationships across locales. Multiple
linear regression is appropriate because the cross-sectional data are non-nested
which a continuous outcome. Hierarchical linear models are necessary to control
for the between-subject variation in the longitudinal models. Fixed models are
appropriate because they extract the between group-differences from the model to
allow the reader to focus on the overall effects of each variable. In these
models, include location metadata like county population size, broadband rates,
and median income to adjust for potentially confounded relationships between
Google search Trends and credible indicators. Identifying these possible
confounded relationships may help to explain why some articles find
relationships between the trends and outcomes while others did not. For linear
regression models, I normalize independent variables so that each variable
across each model is on the same scale and can be compared. In other words,
variables have been centered and scaled to have a mean of zero and standard
deviation of one. Results of these models are in Tables
\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.

@@

@@

Previous research has shown some relationship between Google Search Trends and
political election results. I investigate the relationships between search trends
and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
correlations for Both Hilary Clinton and Donald Trump do not exceed a |0.17|
correlation with the actual percentage of votes for either candidate. In 2020,
results are even less related, with searches for neither Joe Biden nor Donald
Trump holding any real correlation with the 2020 results.

In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
predicting the county percentage of votes for Hillary Clinton. Model 1
demonstrates how well Google Trends predict the votes; while the trend for
'Hillary Clinton' is significantly associated with votes, the model's $r^2$
($r^2$ = 0.027) shows that it does little to help explain the model variance. On
the other hand, adding in demographic features improves the model fit quite
well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in model 3.
Table \ref{tab:pres_2020_analysis} shows this same analysis for the 2020
election and predicts the percentage of votes for Joe Biden. While this model is
analogous to those in Table \ref{tab:pres_2016_analysis}, this model 1
demonstrates how unrelated Google Trends can be from actual outcomes. In
conclusion, I find that Google Trends are an unreliable and invalid indicator of
political support.

@@

>>>>

New sources of digital trace data have led to vast possibilities for social
science research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
Digital trace data are the expansive volumes of information that are now
available with the introduction and widespread adoption of the internet and
include sources such as social media sites, search data, blogs, administrative
data on websites, the internet archives, etc. In short, digital trace data are
the crumbs that are left as a person peruses and interacts in digital spaces.
Scholars have noted that these data provide many new research avenues for social
scientists because they are always on, non-reactive to a researcher's
observation, and very often capture social interactions and relationships, but
warn they can be inaccessible, non-representative, and be prone to drifting due
to algorithmic confounding\citep{salganikBitBitSocial2017}. Before
overenthusiastically embracing these sources and integrating them into our big
data toolkits, social scientists must clearly establish parameters under which
these data sources are appropriate, and for which questions they are useful
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the ``quantity of data does not mean that one can ignore
foundational issues of measurement and construct validity and reliability and
dependencies among data'' \citep[p. 1203]{lazerParableGoogleFlu2014}.

@@

Building on prior research outlining the various issues with different sources
of big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
paper evaluates the construct validity of Google Search Trends as an indicator
of three different cases, namely attitudes, disease prevalence and political
preferences. These three cases will be tested using attitudinal indicators from
the CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
health indicators from the CDC
\citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
\citeyearpar{covid_data}, and political indicators from the historical US
Presidential Election results \citeyearpar{pres_data}. 
% , and the American National Election Survey \citeyearpar{anes_data}.
This paper will contribute
guidance for creating standards of how to use Google Trends for social research,
and identify potential pitfalls that can compromise the analysis including the
focus of this paper, which shows that Google Trends has a lack of ecological
validity.

@@

I will use three categorizations of ways I propose Google Trends could be
utilized for social scientific usage. First, I test Google Trends as an
indicator of attitudinal indicators. After
\citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
utilize the ever-expanding world of big data, Google Trends began slowly
appearing as a data source in sociological and social science research. From
research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020},
protest and anti-Muslim sentiment
\citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural interest.
Extending into social networks and culture,
\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how they saw 'culture' spreads around the globe through the proliferation of
search terms.

@@

Google Search Trends have been utilized to estimate disease prevalence and
population throughout the health sciences. While much of this research has
focused on the COVID-19 pandemic \citep{jimenez_etal20,
jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020,
mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020,
todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021}, other
research has investigated Google Trends as indicators of wellbeing
\citep{brodeurCOVID19LockdownsWellbeing2021,
carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020}, suicidality
\citep{burnettTimeTrendsPublic2020}, vaccination uptake
\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess a
correlation of \> .70 between the IV and DV, ``demonstrating the vast potential
of Google Search as a proxy for monitoring population health'' (p. 3) based on
assumptions that individuals search because of self-diagnosis and to identify
possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.

@@

Various sources have also used Google Trends to forecast political elections and
political attitudes \citep{wolfTrendingRightDirection2018}. For instance,
\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate elections
relate to attention measured by search traffic.
\citet{pradoromanGoogleTrendsPredictor2020} demonstrate how Google Search trends
successfully predicts presidential election results in both the United States
and Canada. Finally, the OECD Development Centre is investigating how Google
data can help elucidate governments' approval in Latin America
\citep{montoyaUsingGoogleData2020}. Overall, the papers cited here find
favorable relationships between Google Trends and voting outcomes and claim that
it is also a valid measure of public attention.

@@

While Google Trends has not been widely used or validated by social scientists,
I am not the first author to investigate its validity. Some researchers have
cautioned against the wide usage of Google Search Trends. For instance,
\citet{asseoTrackingCOVID19Using2020} concludes in their research on COVID-19
case rates and Google searches that the correlation is often spurious and due to
confounding. They even explain that ``searches would result not only from
self-symptoms, but also from interest elicited by media coverage''
\citep[][p.1]{asseoTrackingCOVID19Using2020}.

@@

\citet{cebrian_domenech22} emphasize in their research that there are some
non-negligible issues with the measurement of Google Trends, pointing to errors
within the purview of accuracy, completeness, consistency, and validity, as
outlined in \citet{KarrDataQuality}. 
% I know it is basic stats, but I would provide a footnote explaining each of your terms. 
% Here, these line up with mainline stats but disciplines vary.
\citet{cebrian_domenech22} point not only
to meta issues like the lack of transparency into the sampling methods and
population coverage, but they identify real differences in the data provided by
the Google Trends API for the same researcher-entered query, pointing to likely
internal process used by Google to sample their data to compute the trends.
These authors show that the variability of the results over time for the same
query can alter the results of analysis and forecasting significantly. While the
issue of unreliability isn't unique to the Google Trends API,
\citet{cebrian_domenech22} propose caution in the use of this digital trace data
for other researchers until further research can determine the root cause for
the inaccuracies.
% Yes, big issue. But, it is also seen in machine learning, survey 
% administration, etc. I’d assume one solution for dealing with fiddly 
% output is to just sample repeatedly and do some sort of average, 
% perhaps with a correction if the direction of the error is non random.

Finally, it is important to note that most of the research using Google Trends
as digital trace data do so to indicate population's \textit{attention} to a
search query. Because searches can be done with
% I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online. 
many different intentions, such as information gathering, navigational purposes,
etc., it may be hard to declare that an overall level of engagement with a topic
on Google Search may be indicative of anything more than interest
\citep{da2011search}. To reference Clifford Geertz's invocation of Ryle, we only
know that the search was performed, not whether it indicated a digital wink or
twitch \citeyearpar{geertz1973thick}.
% For a soc audience some sort of reference to the dilemma of interpretation would be interesting.

@@

To test how well Google Trends can be used to indicate other measures, I use
various tests to validate the criterion validity of the trends. Criterion
validity measures how well an \textit{operationalization} of a specific
construct is able to predict a \textit{theoretical representation} of the construct —
the criterion. For this article, I employ concurrent criterion validity which
looks at how Google Trends can predict various criterions in the same time
scale. I gathered geolocated social science data across multiple sources to
address the three areas of inquiry for this paper.  Table
\ref{tab:data-sources-table} outlines which data sources I use in this project
and which trends are matched to each source. In addition, descriptive statistics
for all variables used in these analyses are included in Table \ref{tab:a1_desc_stats}.

\input{tables/paper1/data-sources-table}
\input{tables/paper1/desc_stats}

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification of ``similar population clusters''
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo}.

@@

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse
Survey (HPS) and the 2019 American Community Survey (ACS) 1-year Public Use
Microdata Sample (PUMS) to measure U.S. residents’ intentions to receive the
COVID-19 vaccine if available during May 26, 2021 – June 7, 2021. This dataset
consists of 3,148 observations, one for each U.S. County. The variable measures
the percent of adults in the county who describe themselves as ``unsure'',
``probably not'', or ``definitely not'' going to get a COVID-19 vaccine once one is
available to them. The variable ranges from 4.99\% to 32.33\%.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata, a global online market research firm, for the New York Times from July 2
through 14, 2020 \citep{mask_data}. 250,000 survey respondents were asked, ``How
often do you wear a mask in public when you expect to be within six feet of
another person?''. The NYT weighted each response to create a county level
measure of what percent of the county never, rarely, sometimes, frequently, and
always wore a mask when in public. This dataset consists of 3,148 observations,
one for each U.S. County included in the sample. This measure is purposed to
estimate the percent of adults in the county who never or rarely wear a mask
(range = 0.10\% to 55.80\%).

@@

I also use U.S. COVID-19 rates to validate health and disease related topics. I
retrieve U.S. county-level COVID-19 rates from \citet{covid_data}, who compile
this data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test \citep{gu22, cdc20a}.
However, it is the best measure we have of
actual case rates without extensive adjustments. Case Rate is measured as number
of cases per 100,000 population. Observations vary from a minimum of zero to a
maximum of 1460.46 for each Monday from January 27, 2020, through December 27,
2021. There are 285,986 cases across 3,136 counties and 101 dates. Missing data
were interpolated using The Zoo package for R \citep{zoo}.

@@

In addition to specific measures of interest, I also gathered data on
potentially confounding variables. The first seven of these variables come from
the 2010-2019 5-year American Community Surveys \citep{acs2019, acs2018,
acs2017, acs2016, acs2015, acs2014, acs2013, acs2012, acs2011, acs2010}. These
data include total population, population density, unemployment rate for those
sixteen years old and over, median county income, average commute time, percent
of households living under the poverty line, and percent above 65 years old. In
addition, some models employ the U.S. Current Population Survey \& American
Community Survey Geographic Estimates of Internet Use, 1997-2018
\citep{internet_use} to estimate households with broadband internet
subscriptions. This final variable is an attempt to capture the latent
propensity to use the internet for information search.

@@

As an additional criteria to evaluate the strength of the relationships, I
employ multiple linear regression (for cross-sectional datasets) and fixed
effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
datasets) to identify the strength of relationships across locales. Multiple
linear regression is appropriate because the cross-sectional data are non-nested
with a continuous outcome. Hierarchical linear models are necessary to control
for the between-subject variation in the longitudinal models. Fixed models are
appropriate because they extract the between group-differences from the model to
allow the reader to focus on the overall effects of each variable. In these
models, include location metadata like county population size, broadband rates,
and median income to adjust for potentially confounded relationships between
Google search Trends and credible indicators. 'County level fips mean' is included
in each model to control for within-group variation of the outcome, a standard practice
in mixed effects modeling. Identifying these possible
confounded relationships may help to explain why some articles find
relationships between the trends and outcomes while others did not. For linear
regression models, I normalize independent variables so that each variable
across each model is on the same scale and can be compared. In other words,
variables have been centered and scaled to have a mean of zero and standard
deviation of one. Results of these models are in Tables
\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}. 
In addition to coefficients, each table include the marginal $R^2$ and sometimes 
a conditional $R^2$, the first describes the proportion of variance explained by the fixed factor alone and the latter the fixed and random factors.

@@

% # TODO All variables have been standardized, right? So when you say an effect is ``small,'' could you give an illustration? E.g., translate it back into metric coefficients? For example, ''for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?  The main thing is to have an intuitive description of what the effect size is, not just to look at a standardized coefficient of .002.

@@

Previous research has shown some relationship between Google Search Trends and
political election results. I investigate the relationships between search trends
and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
correlations of search trends with actual percentage of votes for Both Hilary
Clinton and Donald Trump do not exceed a |0.17| correlation for either candidate. In 2020,
results are even less related, with searches for neither Joe Biden nor Donald
Trump holding any real correlation with the 2020 results.

% The sign in Model 1 is interesting. The more likely a voter is to vote against Clinton, the more they search for her? (Obsessive?) Is that right? Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: ''According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
predicting the county percentage of votes for Hillary Clinton. Model 1
demonstrates how well Google Trends predict the votes; while the trend for
'Hillary Clinton' is significantly associated with votes, the model's $r^2$
($r^2$ = 0.027) shows that it does little to help explain the model variance. On
the other hand, adding in demographic features improves the model fit quite
well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in model 3.
Table \ref{tab:pres_2020_analysis} shows this same analysis for the 2020
election and predicts the percentage of votes for Joe Biden. While this model is
analogous to those in Table \ref{tab:pres_2016_analysis}, this model 1
demonstrates how unrelated Google Trends can be from actual outcomes. In
conclusion, I find that Google Trends are an unreliable and invalid indicator of
political support.

@@

%  TODO What might be some limitations of your analysis? Are there some issues raised here that should be further explored in subsequent research?
